Guided Proofreading of Automatic Segmentations for Connectomics

### 2018-03-28 paper/conclusion.tex
Update author list.
Update camera-ready version.

\vspace{-2mm}
\section{Conclusions}

@@

Manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. We provide our framework and data as free and open research\footnote{\scriptsize{\url{http://rhoana.org/guidedproofreading/}}}.

@@

\vspace{-1mm}
\section*{Acknowledgements}
%We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier. This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by the Intelligence Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center (DoI/IBC) contract number D16PC00002.
We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier. This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by IARPA contract D16PC00002.

>>>>

%\vspace{-2mm}
\section{Conclusions}

@@

Manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. We provide our framework and data as free and open research\footnote{\scriptsize{http://rhoana.org/guidedproofreading/}}.

@@

%\vspace{-1mm}
\section*{Acknowledgements}
%We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier. This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by the Intelligence Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center (DoI/IBC) contract number D16PC00002.
We thank Stephen Plaza for detailed explanations of \emph{Focused Proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier. We also thank Deqing Sun and the wider Harvard VCG group for constructive feedback. This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by IARPA contract D16PC00002.

### 2018-03-28 paper/evaluation.tex
Update author list.
Update camera-ready version.

\paragraph{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex, acquired using ssEM. The dataset resolution is $3\times3\times30~\text{nm}^3\text{/voxel}$. Image data and a manually-labeled expert `ground truth' segmentation is publicly available\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.

\paragraph{AC4 subvolume.} This is part of a publicly-available dataset of mouse cortex that was published for the ISBI 2013 challenge ``SNEMI3D: 3D Segmentation of neurites in EM images''. The dataset resolution is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM. Haehn~\etal~\cite{haehn_dojo_2014} found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes, and used it for their interactive connectomics proofreading tool experiments. We use their publicly available data, labeled ground truth, and study findings\footnote{\scriptsize{\url{http://rhoana.org/dojo/}}}.

@@

\vspace{-4mm}

@@

\vspace{-3mm}

>>>>

\paragraph{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex, acquired using ssEM. The dataset resolution is $3\times3\times30~\text{nm}^3\text{/voxel}$. Image data and a manually-labeled expert `ground truth' segmentation is publicly available\footnote{\scriptsize{https://software.rc.fas.harvard.edu/lichtman/vast/}}.

\paragraph{AC4 subvolume.} This is part of a publicly-available dataset of mouse cortex that was published for the ISBI 2013 challenge ``SNEMI3D: 3D Segmentation of neurites in EM images''. The dataset resolution is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM. Haehn~\etal~\cite{haehn_dojo_2014} found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes, and used it for their interactive connectomics proofreading tool experiments. We use their publicly available data, labeled ground truth, and study findings\footnote{\scriptsize{http://rhoana.org/dojo/}}.

@@

%\vspace{-4mm}

@@

%\vspace{-3mm}

### 2018-03-28 paper/guidedproofreading_final.tex
Update author list.
Update camera-ready version.

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,linkcolor=blue,citecolor=blue,bookmarks=false]{hyperref}

@@

\author[1,2]{Daniel Haehn\thanks{Corresponding author,  \url{haehn@seas.harvard.edu}}}
\author[1,2]{Verena Kaynig}
\author[3]{James Tompkin}
\author[2]{Jeff W. Lichtman}
\author[1,2]{Hanspeter Pfister}
\affil[1]{Harvard's Paulson School of Engineering and Applied Sciences}
\affil[2]{Harvard's Center for Brain Science}
\affil[3]{Brown University}

>>>>

\makeatletter
\renewcommand\AB@affilsepx{~~~~~\protect\Affilfont}
\makeatother

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,linkcolor=blue,citecolor=blue,bookmarks=false]{hyperref}

@@

%\author[1,2]{Daniel Haehn\thanks{Corresponding author,  \url{haehn@seas.harvard.edu}}}
%\author[1,2]{Verena Kaynig}
%\author[3]{James Tompkin}
%\author[2]{Jeff W. Lichtman}
%\author[1,2]{Hanspeter Pfister}
%\affil[1]{Harvard's Paulson School of Engineering and Applied Sciences}
%\affil[2]{Harvard's Center for Brain Science}
%\affil[3]{Brown University}

\author[1]{Daniel Haehn\thanks{Corresponding author,  haehn@seas.harvard.edu}}
\author[1]{Verena Kaynig}
\author[2]{James Tompkin}
\author[1]{Jeff W. Lichtman}
\author[1]{Hanspeter Pfister}
\affil[1]{Harvard University}\affil[2]{Brown University}
